---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753ho0040SP24)
```

# mybin Function
```{r}
MATH4753ho0040SP24::mybin(iter=100,n=10, p=0.7)
```

Binomial simulation function that returns a barplot of a binomial simulation based on n, number of iterations, and probability.

# ntickets Function
```{r}
MATH4753ho0040SP24::ntickets(400, 0.02, 0.95)
```

Ticket function that returns a named list containing nd, nc, N, p and gamma - where nd is calculated using the discrete distribution and nc is the same calculated with normal approximation.

# myboot2 Function
```{r}
sam=rnorm(25,mean=25,sd=10)
MATH4753ho0040SP24::myboot2(iter=10000,alpha=0.05,sam, cx=1.5,xlab="mean")
```

Bootstrap function that returns a number of plots, point and interval estimates and useful output in the form of a list.

# mymlbeta Function
```{r}
MATH4753ho0040SP24::mymlbeta(x=rbeta(100,shape1=2,shape2=5),alpha=seq(1,4,length=100), beta=seq(2,8,length=100),lwd=2,labcex=1)
```

Beta function that returns a beta distribution

# FIREDAM data set
```{r}
data(fire)
head(fire)
names(fire)
```

FIREDAM.csv data set is saved into the package and displays the head() and names() functions to test it.
